Cleaning up Crime

### 2024-08-03 code/eda-code/eda.qmd
Project Assignment 4 and 5 submission. Mostly ready for final submission, need to add narrative to eda and stat qmd files

---
title: "An example exploratory analysis script"
date: "2024-02-07"
output: html_document
---

@@

```{r setup}
#load needed packages. make sure they are installed.
pacman::p_load(here, knitr, tidyverse, skimr, fpp2)
theme_set(theme_minimal())
```

@@

```{r}
d1 <- readRDS(here('data','processed-data','processed-crime.rds'))
zips <- read_csv(here('data','raw-data','austin-zip-codes.csv'))
```

@@

```{r}
summary(zips)
head(zips)
str(zips)
skim(zips)
```

@@

```{r}
d1 %>% group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line()
```

@@

```{r}
d1 %>% filter(Occurred.Date <= '2023-12-31') %>%
  mutate(Occurred.Date = trunc.Date(Occurred.Date, 'months')) %>% 
  group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line()
```

@@

@@

# Notes

Including this sandbox chunk where I can experiment with code as needed.
ARIMA is not going well, mostly due to seasonal nature of data. Filtering the time range might help, or isolating other variables to do things liek predict certain types of crime instead.

```{r sandbox}

d1 %>% mutate(Category.Description = if_else(Category.Description == '', 'NA/Unknown', Category.Description)) %>% group_by(Category.Description, Highest.Offense.Description) %>% summarize(cnt = n()) %>% pivot_wider(names_from = Category.Description, values_from = cnt)

temp <- d1 %>%
         mutate(Occurred.Date = trunc.Date(Occurred.Date, 'months')) %>% 
         group_by(Occurred.Date) %>% 
         summarize(
             cnt = n()
         ) %>% as.data.frame() %>% 
  filter(year(Occurred.Date) != 2024)
rownames(temp) <- temp$Occurred.Date
temp <- temp %>% select(cnt)

temp2 <- temp %>% as.ts()
Acf(temp2)
Box.test(temp2, lag = 12, type = 'Ljung-Box')
auto.arima(temp2)
temp2 %>% log() %>% diff(12) %>% diff() %>% diff() %>% diff() %>% diff() %>% diff() %>% Acf()
```

>>>>

---
title: "An example exploratory analysis script"
date: "2024-07-31"
output: html_document
---

@@

```{r setup}
#load needed packages. make sure they are installed.
pacman::p_load(here, knitr, tidyverse, skimr, fpp2, tigris, plotly, viridis, transformr, htmlwidgets, gt, gtExtras, widgetframe)
theme_set(theme_minimal())
```

@@

```{r}
d1 <- readRDS(here('data','processed-data','processed-crime.rds'))
tig_zips <- zctas(cb=TRUE, starts_with = c(unique(d1$Zip.Code)), year = 2020)
```

@@

```{r}
summary(tig_zips)
head(tig_zips)
str(tig_zips)
skim(tig_zips)
```

@@

```{r}
dayline <- d1 %>% group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line() +
  labs(title = 'Austin Crime Over Time', x = 'Time of Occurence (by day)', y = 'Count')

dayline

ggsave(here('results', 'figures', 'static-plots', 'crime-by-day.png'), dayline)
```

@@

```{r}
monthline <- d1 %>% filter(Occurred.Date <= '2024-03-31') %>%
  mutate(Occurred.Date = trunc.Date(Occurred.Date, 'months')) %>% 
  group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line() +
  labs(title = 'Austin Crime Over Time', x = 'Time of Occurence (by month)', y = 'Count')

monthline

ggsave(here('results', 'figures', 'static-plots', 'crime-by-month.png'), monthline)
```

@@

```{r}
murdline <- d1 %>% filter(Occurred.Date <= '2024-03-31', Crime.Category == 'MURDER') %>%
  mutate(Occurred.Date = trunc.Date(Occurred.Date, 'months')) %>% 
  group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line() +
  labs(title = 'Austin Murder Over Time', x = 'Time of Occurence (by month)', y = 'Count')

murdline

ggsave(here('results', 'figures', 'static-plots', 'murder-by-time.png'), murdline)
```
*ADD COMMMENTARY LATER: NUMBER OF FIRST QUARTER HOMICIDES MATCHES ARTICLE FOR 2020 AND 2023, BUT NOT 2024. ARTICLE LIKELY NOT COUNTING INTOX MANSLAUGHTER OR JUSTIFIED HOMICIDE. KEPT THOSE BECAUSE FBI CATEGORIZATION COUNTS MANSLAUGHTER.*

@@

```{r}
yearlyCrime <- d1 %>% mutate(
  Zip.Char = as.character(Zip.Code),
  years = year(Occurred.Date),
  years = as.character(years)
  ) %>% filter(years != 2024) %>% 
  group_by(Zip.Char, years) %>% 
  summarize(crim.count  = n()) %>% 
  ungroup() %>% 
  as.data.frame()
  #filter(count >= 500) %>%
  #filter(Zip.Char == '78741') %>%

allYrsZips <- expand.grid(years = unique(yearlyCrime$years), Zip.Char = unique(yearlyCrime$Zip.Char))

yearlyCrimeAll <- left_join(allYrsZips, yearlyCrime, by = join_by(Zip.Char, years))  %>% 
  inner_join(tig_zips, by = join_by(Zip.Char == ZCTA5CE20)) %>% 
  mutate(crim.count = ifelse(is.na(crim.count), 0, crim.count))

```{r}
cpeth <- yearlyCrimeAll %>% filter(crim.count >= 50) %>% 
  ggplot() +
  geom_sf(aes(geometry = geometry, fill = crim.count, frame = years, text = paste(Zip.Char, '<br>', crim.count))) +
  scale_fill_gradient2(low = "#E0144C", mid = '#FFFFFF', high = "#000067", midpoint = -5000, 
                       trans = 'reverse') +
  theme_classic() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        line = element_blank(),
        plot.title = element_text(hjust = 0, size = 15)) +
  labs(fill = 'Crime Count',
       title = 'Crime by Location Over Time')

cplotly <- cpeth %>% ggplotly() %>% 
  layout(hoverlabel = text) %>% 
  animation_opts(1500, 1) %>% 
  animation_slider(currentvalue = list(visible = FALSE)) %>% 
  animation_button(x = 0, xanchor = "left", y = 0, yanchor = "bottom")
cplotly

saveWidget(frameableWidget(cplotly), here('results', 'figures', 'html-widgets', 'crime-location.html'))
```

```{r}
yearlyMurder <- d1 %>% mutate(
  Zip.Char = as.character(Zip.Code),
  years = year(Occurred.Date),
  years = as.character(years)
  ) %>% filter(years != 2024, Crime.Category == 'MURDER') %>% 
  group_by(Zip.Char, years) %>% 
  summarize(murder.count  = n()) %>% 
  ungroup() %>% 
  as.data.frame()

yearlyMurderAll <- left_join(allYrsZips, yearlyMurder, by = join_by(Zip.Char, years))  %>% 
  inner_join(tig_zips, by = join_by(Zip.Char == ZCTA5CE20)) %>% 
  mutate(murder.count = ifelse(is.na(murder.count), 0, murder.count))
```

```{r}
cpeth2 <- yearlyMurderAll %>% #filter(murder.count >= 1) %>% 
  ggplot() +
  geom_sf(aes(geometry = geometry, fill = murder.count, frame = years)) +
  #geom_sf_label(aes(label = paste(Zip.Char, '<br>', murder.count))) +
  scale_fill_gradient2(low = "#E0144C", mid = '#FFFFFF', high = "#000067", 
                       trans = 'reverse') +
  theme_classic() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        line = element_blank(),
        plot.title = element_text(hjust = 0, size = 15)) +
  labs(fill = 'Murder Count',
       title = 'Murder by Location Over Time')

cplotly2 <- cpeth2 %>% ggplotly() %>% 
  layout(hoverlabel = text) %>% 
  animation_opts(1500, 1) %>% 
  animation_slider(currentvalue = list(visible = FALSE)) %>% 
  animation_button(x = 0, xanchor = "left", y = 0, yanchor = "bottom")
cplotly2
```

```{r}
catYearly <- d1 %>% mutate(
  years = year(Occurred.Date)
  #years = as.character(years)
  ) %>% filter(years != 2024) %>% 
  group_by(Crime.Category, years) %>% 
  summarize(crim.count  = n()) %>% 
  ungroup() %>% 
  as.data.frame()

allYrsCats <- expand.grid(years = unique(catYearly$years), Crime.Category = unique(catYearly$Crime.Category))

yearlyAllCats <- left_join(allYrsCats, catYearly, by = join_by(Crime.Category, years))  %>% 
  mutate(crim.count = ifelse(is.na(crim.count), 0, crim.count))

catbar <- yearlyAllCats %>%  
  ggplot() +
  geom_bar(aes(y= fct_reorder(Crime.Category, crim.count), x = crim.count, frame = years), stat = 'identity') +
  labs(x = 'Count of Offense', y = 'Offense Description', title = 'Frequncy of Crim by Offense Category')
  #scale_x_continuous(transform = 'log')
catbar

fig <- plot_ly(yearlyAllCats,
  x = ~crim.count,
  y = ~fct_reorder(Crime.Category, crim.count),
  type = 'bar',
  showlegend = F,
  frame = ~years,
  marker = list(color = '#000067')
)

catbarly <- fig %>% 
  layout(
    yaxis = list(
      title = '', tickangle = -30, tickfont = list(size = 8)
      ), 
    xaxis = list(
      title = 'Count of Occurence' 
    ),
    title = list(
      text = 'Yearly Occurence of Crime by Category',
      y = 0.99, x = 0.1, xanchor = 'left', yanchor = 'top',
      font = list(
        size = 18
      )
      )
    )

catbarly

saveWidget(frameableWidget(catbarly), here('results', 'figures', 'html-widgets', 'crime-cat.html'))
```

First table is intended to act as a translation key between description and category, but also serves well to illustrate the motivation behind the categorizations.
```{r}
RecatTable <- d1 %>% 
  filter(year(Occurred.Date) < 2024) %>% 
  mutate(
  Occur.Years = trunc.Date(Occurred.Date, 'years')
  ) %>% 
  group_by(Crime.Category, Highest.Offense.Description, Occur.Years) %>% 
  summarize(
    Count = n(),
    .groups = 'drop'
  ) %>% 
  arrange(by = Occur.Years) %>%
  group_by(Crime.Category, Highest.Offense.Description) %>% 
  summarize(
    mean = mean(Count),
    sd = sd(Count),
    sum = sum(Count),
    .groups = 'drop'
  ) %>% 
  gt() %>% 
  tab_header(
    title = md('**Crime Recategorization Key**')
    ) %>% 
  cols_label(
    Crime.Category = md('**New Category**'),
    Highest.Offense.Description = md('**Original Description**'),
    mean = md('**Mean Occurrence Across Years**'),
    sd = md('**Standard Deviation of Yearly Occurrence**'),
    sum = md('**Total Occurrences**')
  ) %>% 
  fmt_number(columns = mean:sd, decimals = 1) %>% 
  opt_interactive()

gtsave(RecatTable, 'recat-table.html', here('results', 'figures', 'html-widgets'))
#saveWidget(frameableWidget(RecatTable), here('results', 'figures', 'html-widgets', 'recat-table.html'))
RecatTable
```

Plot highlights the advantages in the categorization, with inclusion of sparklines for clarity on movement over time.
```{r}
newCatTable <- d1 %>%
  filter(year(Occurred.Date) < 2024) %>% 
  mutate(
  Occur.Years = trunc.Date(Occurred.Date, 'years')
  ) %>% 
  group_by(Crime.Category, Occur.Years) %>% 
  summarize(
    Count = n(),
    .groups = 'drop'
  ) %>% 
  arrange(by = Occur.Years) %>%
  group_by(Crime.Category) %>% 
  summarize(
    mean = mean(Count),
    sd = sd(Count),
    list = list(Count),
    .groups = 'drop'
  ) %>% 
  gt() %>% 
  tab_header(
    title = md('**Crime Categories Over Time**')
    ) %>% 
  cols_label(
    Crime.Category = md('**Crime Category**'),
    mean = md('**Mean Occurrence Across Years**'),
    sd = md('**Standard Deviation of Yearly Occurrence**'),
    list = md('**Change Over Time**')
  ) %>% 
  fmt_number(columns = mean:sd, decimals = 1) %>% 
  gtExtras::gt_plt_sparkline(column = list, type = 'ref_iqr', same_limit = FALSE) %>% 
  tab_footnote('Note: Sparklines have independent axes, comparisons should not be considered across different categories')
gtsave(newCatTable, 'new-cat-table.html', here('results', 'figures', 'html-widgets'))
newCatTable

### 2024-08-03 code/processing-code/processingfile.qmd
Project Assignment 4 and 5 submission. Mostly ready for final submission, need to add narrative to eda and stat qmd files

@@

```{r}
processeddata <- d2
```

@@

```{r Sandbox, echo=FALSE}
#rawdata %>% filter(Occurred.Date.Time == '')

rawdata %>% mutate(
  test = (str_sub(as.character(Occurred.Time), -2, -1)
          %>% as.numeric()),
  Occurred.Date = mdy(Occurred.Date)
  ,Report.Date = mdy(Report.Date)
  ,Occurred.Date.Time = parse_date_time(Occurred.Date.Time,'%m/%d/%Y %I:%M:%S %p')
  ,Report.Date.Time = parse_date_time(Report.Date.Time,'%m/%d/%Y %I:%M:%S %p')
  ,Clearance.Date = mdy(Clearance.Date)
  ) %>% mutate(
    Occurred.Time = if_else(
      is.na(Occurred.Time) | test >= 60, 
      if_else(
        Occurred.Date == Report.Date,
        if_else(
          is.na(Report.Time), 
          2359, Report.Time
          ), 2359
        ), if_else(
          Occurred.Time == 2400, 
          2359, Occurred.Time
          ) 
      ) %>% as.character()
    ) %>% mutate(
      Occurred.Time = paste0('000',Occurred.Time,'00') %>% 
        str_sub(.,-6,-1) %>% 
        parse_time('%H%M%S')
      ) %>% select(-test)
```

>>>>

### And We're Back

The string variable `Highest.Offense.Description` was just too rich to pass up. It would make for an excellent categorical variable however there are over 400 categories going off the variable as-is. `UCR.Category` is a very nice alternative with only a few levels to the category, but the field is mostly empty due to the nature of the variable. It represent an FBI Categorization known as Uniform Crime Reporting (UCR) for the most serious of crimes. So I decided to take the matter into my own hands. Number one, I would create a new field that categorizes the crime myself, based on categorizations in the UCR program. If the observation had values in the UCR field, I would take that one, if it did not, I impute a category based on the description in the Highest Offense Description field. This was mostly done through brute force, with string detection and research in two places, the [FBI UCR archive](https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/offense-definitions) (2019 was not the only year that had information on the categorizations but it was the most in a quick reference format), and the [Texas Capitol Statutes website](https://statutes.capitol.texas.gov/). I feel the need to address this up front, I am absolutely not a criminologist, these categorizations are solely for the sake of making my analysis easier. I think of this as grouping the crime descriptions from the perspective of a layman, me, because ultimately the average person observing crime statistics will roughly as little knowledge about them as I do. An expert could and would do a much better job than I did, but that wasn't readily available so I worked with what I had. Famous last words of an analyst.
```{r}
unique(d2$Category.Description) %>% as.data.frame()
unique(d2[c('Category.Description','Highest.Offense.Description')]) %>% as.data.frame()
```

```{r}
UCRCats <- d2 %>% filter(Category.Description != '') %>% select(Category.Description) %>% unique()
row.names(UCRCats) <- NULL
UCRCats <- UCRCats[c(7,1,4,5,6,3,2),]
row.names(UCRCats) <- NULL

defCats <- rbind(CHILD = str_flatten(c('CHILD', 'MINOR', 'TRUANCY', 'NONSUPPORT'), collapse = '|') # Sex Offense involving a Child, Child Abuse/ Endangerment, Injury/Harm of Vulnerable Persons*
                 ,HARASSMENT = str_flatten(c('HARASSMENT', 'PROWLER', 'STALKING'), collapse = '|') # General Harassment
                 ,'SEX OFFENSE'= str_flatten(c('SEX', 'INVASIVE', 'INTIMATE', 'PROSTITUTION', 'OBSC', 'ADULT', 'BESTIALITY', 'INDECEN', 'ENTIC', 'PORN', 'SOLICITATION OF', 'GROOMING'), collapse = '|') # Sexual Offense
                 ,'DISORDERLY CONDUCT' = str_flatten(c('DOC', 'LEWD', 'URINATING', 'RECKLESS CONDUCT', 'ILLUMIN', 'CORPSE', 'ANIMAL', 'RIOT', 'PROCESSION'), collapse = '|') #Disorderly Conduct
                 ,VOCO = str_flatten(c('VOCO', 'ORDINANCE', 'CURFEW', 'CAMP', 'AMPLIFIED', 'GLASS', 'CITY ORD'), collapse = '|') # Violation of City Ordinance
                 ,'SIMPLE ASSAULT' = str_flatten(c('ASSAULT','ASLT$', 'ASSLT', 'PROD', 'ATTACK BY DOG', 'VIOLENCE', 'HAZING', 'SUICIDE', 'CONFRONT'), collapse = '|') # Simple Assault/ ASSAULTIVE
                 ,TRESPASSING = str_flatten(c('TRESPASS', 'LOITER', 'SLEEP', 'BEG'), collapse = '|') # TRESPASSING
                 ,'LARGE SCALE THREAT' = str_flatten(c('THREAT'), collapse = '|') # Large Scale Threat
                 ,'GENERAL DISTURBANCE' = str_flatten(c('DISTURBANCE'), collapse = '|') # General Disturbance
                 ,'DRUG RELATED' = str_flatten(c('DRUG', 'SUB', 'MARIJUANA', 'INHALANT', 'TOBACCO', 'PRESCRIPTION'), collapse = '|') #Drug Related
                 ,'FRAUD' = str_flatten(c('FRAUD', 'FALSE', 'IMPERSON', 'FORGE', 'COUNTERFEITING', 'TAMPER', 'LABEL', 'PIGEON', 'MEDICINE', 'NAME'), collapse = '|') #Fraud, Unlawful Deception
                 ,'ALCOHOL RELATED' = str_flatten(c('ALCOHOL', 'LIQ', 'DWI', 'DUI', 'WHILE INTOX', 'BWI'), collapse = '|') # Alcohol Related
                 ,'HARM OF VULNERABLE PERSONS' = str_flatten(c('INJ', 'ELDER'), collapse = '|') #Injury/Harm of Vulnerable Persons*
                 ,'NON-COMPLIANCE' = str_flatten(c('WARR', 'BAIL', 'IDENTIFY', 'PROBATION', 'INTER', '911', 'ARREST', 'EVAD', 'PERJURY', 'PAROLE','RETALIATION', 'ESCAPE', 'HINDERING', 'BOND', 'CONTEMPT'), collapse = '|') # Warrant, Non Compliance
                 ,'CRIMINAL MISCHIEF' = str_flatten(c('MISCHIEF', 'ARSON', 'DAMAGE', 'GRAFFITI', 'DESECRATION'), collapse = '|') # CRIMINAL MISCHIEF
                 ,'UNLAWFUL RESTRAINT' = str_flatten(c('KIDNAP', 'RESTRAINT'), collapse = '|') # Unlawful Restraint
                 ,'WEAPON RELATED' = str_flatten(c('WEAPON', 'FIREARM', 'EXPLOSIVE', 'UCW', 'KNIFE', 'CARRY', 'HANDGUN'), collapse = '|') # WEAPON RELATED
                 ,'PROTECTIVE ORDER' = str_flatten(c('ORDER'), collapse = '|') #PROTECTIVE/ RESTRAINING ORDER
                 ,'FINANCIAL CRIME' = str_flatten(c('CRED', 'DEBIT', 'MONEY', 'BANK'), collapse = '|') # FINANCIAL CRIME
                 ,LITTERING = str_flatten(c('LITTER', 'DUMP', 'WASTE', 'REFRIGERATOR'), collapse = '|') #LITTERING
                 ,'CRIMINAL CONSPIRACY' = str_flatten(c('CRIMINAL SOLICITATION', 'ABATE', 'ORGANIZED', 'CONSPIR'), collapse = '|') # CRIMINAL CONSPIRACY
                 ,'ABUSE OF OFFICE' = str_flatten(c('OFFICIAL', 'PRISONER'), collapse = '|') # ABUSE OF OFFICE
                 ,'GAMBLING RELATED' = str_flatten(c('GAMBL'), collapse = '|') # GAMBLING RELATED
                 ,THEFT = str_flatten(c('RENTAL CAR'), collapse = '|')# THEFT
                 ,MURDER = str_flatten(c('MANSLAUGHTER', 'HOMICIDE'), collapse = '|') # MURDER (MANSLAUGHTER INCLUDED BECAUSE THAT'S HOW FBI CATS)
                 ,BRIBERY = str_flatten(c('BRIBE', 'COERCION OF PUBLIC SERVANT', 'GIFT'), collapse = '|') # BRIBERY
                 ,OTHER = str_flatten(c('IMMIGRATION', 'ALIEN', 'OTHER', 'DISRUPTION OF CLASSES', 'AIRPORT', 'INSTRUMENT','SCHOOLS', 'MASSAGE', 'WATER', 'AWOL', 'DESERTION', 'RENDER'), collapse = '|')# OTHER
                 )%>% as.data.frame()
defCats$Cat <- rownames(defCats)
rownames(defCats) <- NULL  
colnames(defCats) <- c('strSearch', 'Cats')

d3 <- d2 %>% 
    mutate(Crime.Category = if_else(Category.Description == '', 
                                    str_extract(Highest.Offense.Description, str_flatten(toupper(UCRCats), collapse = '|')), 
                                    toupper(Category.Description)
                                    )
          ,Crime.Category = if_else(is.na(Crime.Category),
                                    case_when(
                                      str_detect(Highest.Offense.Description,defCats[1,1]) == TRUE ~ defCats[1,2],
                                      str_detect(Highest.Offense.Description,defCats[2,1]) == TRUE ~ defCats[2,2],
                                      str_detect(Highest.Offense.Description,defCats[3,1]) == TRUE ~ defCats[3,2],
                                      str_detect(Highest.Offense.Description,defCats[4,1]) == TRUE ~ defCats[4,2],
                                      str_detect(Highest.Offense.Description,defCats[5,1]) == TRUE ~ defCats[5,2],
                                      str_detect(Highest.Offense.Description,defCats[6,1]) == TRUE ~ defCats[6,2],
                                      str_detect(Highest.Offense.Description,defCats[7,1]) == TRUE ~ defCats[7,2],
                                      str_detect(Highest.Offense.Description,defCats[8,1]) == TRUE ~ defCats[8,2],
                                      str_detect(Highest.Offense.Description,defCats[9,1]) == TRUE ~ defCats[9,2],
                                      str_detect(Highest.Offense.Description,defCats[10,1]) == TRUE ~ defCats[10,2],
                                      str_detect(Highest.Offense.Description,defCats[11,1]) == TRUE ~ defCats[11,2],
                                      str_detect(Highest.Offense.Description,defCats[12,1]) == TRUE ~ defCats[12,2],
                                      str_detect(Highest.Offense.Description,defCats[13,1]) == TRUE ~ defCats[13,2],
                                      str_detect(Highest.Offense.Description,defCats[14,1]) == TRUE ~ defCats[14,2],
                                      str_detect(Highest.Offense.Description,defCats[15,1]) == TRUE ~ defCats[15,2],
                                      str_detect(Highest.Offense.Description,defCats[16,1]) == TRUE ~ defCats[16,2],
                                      str_detect(Highest.Offense.Description,defCats[17,1]) == TRUE ~ defCats[17,2],
                                      str_detect(Highest.Offense.Description,defCats[18,1]) == TRUE ~ defCats[18,2],
                                      str_detect(Highest.Offense.Description,defCats[19,1]) == TRUE ~ defCats[19,2],
                                      str_detect(Highest.Offense.Description,defCats[20,1]) == TRUE ~ defCats[20,2],
                                      str_detect(Highest.Offense.Description,defCats[21,1]) == TRUE ~ defCats[21,2],
                                      str_detect(Highest.Offense.Description,defCats[22,1]) == TRUE ~ defCats[22,2],
                                      str_detect(Highest.Offense.Description,defCats[23,1]) == TRUE ~ defCats[23,2],
                                      str_detect(Highest.Offense.Description,defCats[24,1]) == TRUE ~ defCats[24,2],
                                      str_detect(Highest.Offense.Description,defCats[25,1]) == TRUE ~ defCats[25,2],
                                      str_detect(Highest.Offense.Description,defCats[26,1]) == TRUE ~ defCats[26,2],
                                      str_detect(Highest.Offense.Description,defCats[27,1]) == TRUE ~ defCats[27,2],
                                      .default = Crime.Category
                                    ),
                                    Crime.Category
          )
          ,Crime.Category = if_else(Crime.Category == 'CHILD',
                                    case_when(
                                      str_detect(Highest.Offense.Description,defCats[3,1]) == TRUE ~ 'SEX OFFENSE INVOLVING A CHILD',
                                      .default = 'HARM OF VULNERABLE PERSONS'
                                    ),
                                    Crime.Category
                                    )
          ,Crime.Category = if_else(Highest.Offense.Description == 'JUSTIFIED HOMICIDE', 'JUSTIFIED HOMICIDE', Crime.Category)
          )
d3 %>% select(Highest.Offense.Description, Category.Description, Crime.Category) %>% head(100)
d3 %>% dim()

d3 %>% group_by(Crime.Category, Category.Description) %>% summarize(
  cnt = n()
)

d3 %>% filter(!is.na(Crime.Category)) %>%
  #,Category.Description == '') %>% 
  #select(Crime.Category, Highest.Offense.Description) %>% 
  group_by(Crime.Category) %>%  #, Highest.Offense.Description) %>% 
  summarize(
    cnt = n()
  ) %>% 
  arrange(by = cnt)
```

@@

```{r}
processeddata <- d3
```

@@
